\huge Tor's Usability for Censorship Circumvention

### 2016-04-15 pets2017-paper/pets2017-paper.tex
find out basics on summary, proxy, and progress edges.

\begin{figure}
\centering
\includegraphics{topology}
\caption{
The chain of components involved in connecting to a website over Tor.
Most users do not need a proxy;
similarly only those users who face a censor need a bridge.
In the diagram, ``Tor'' represents all three anonymizing hops through the Tor network.
We have shown the bridge as a separate component
because of the special role it plays.
When a bridge is used, it takes the place of the first Tor hop.
}
\label{fig:topology}
\end{figure}

@@

\subsection{Results} 
Results from statistical analyses say: 
\begin{itemize} 
	\item{{\bfseries impact of censorship environment on success rate is not significant.} 
	Kruskal-Wallis, chi-squared = 4.7059, df = 2, p-value = 0.09509}
	\item{{\bfseries impact of censorship environment on time to completion is significant.} 
	Kruskal-Wallis, chi-squared = 64.565, df = 2, p-value = 9.547e-15}
	\item{{\bfseries impact of configuration version on success rate is not significant.}
	Mann-Whitney, W = 5.5, p-value = 0.8248}
	\item{{\bfseries impact of configuration interface on time to completion is not significant.} 
	Mann-Whitney, W = 991, p-value = 0.3197}
\end{itemize}

A logistic regression model showing effects of censorship environment, interface version,
and recruitment pool on success finds that a difficult censorship environment is the most
significant factor in a participant failing. Xlab participants were more likely to succeed. 
Participants with the old version of the interface were more likely to fail.

@@

A linear regression model showing effects of censorship environment, interface version, 
and recruitment pool on success finds that a difficult censorship environment is the most
significant factor in taking a long time to complete the task. Participants with the old version
of the interface and participants recruited from Xlab were likely to take longer.

>>>>

\begin{figure}
\centering
\includegraphics{topology.pdf}
\caption{
The chain of components involved in connecting to a website over Tor.
Most users do not need a proxy;
similarly only those users who face a censor need a bridge.
In the diagram, ``Tor'' represents all three anonymizing hops through the Tor network.
We have shown the bridge as a separate component
because of the special role it plays.
When a bridge is used, it takes the place of the first Tor hop.
}
\label{fig:topology}
\end{figure}

@@

\subsection{Results}

%basic statistics (BAD SO FAR)
Results from statistical analyses say: 
\begin{itemize} 
	\item{{\bfseries impact of censorship environment on success rate is not significant.} 
	Kruskal-Wallis, chi-squared = 4.7059, df = 2, p-value = 0.09509}
	\item{{\bfseries impact of censorship environment on time to completion is significant.} 
	Kruskal-Wallis, chi-squared = 64.565, df = 2, p-value = 9.547e-15}
	\item{{\bfseries impact of configuration version on success rate is not significant.}
	Mann-Whitney, W = 5.5, p-value = 0.8248}
	\item{{\bfseries impact of configuration interface on time to completion is not significant.} 
	Mann-Whitney, W = 991, p-value = 0.3197}
\end{itemize}

% impacts of adding in a summary page 
adding in a summary screen causes people to think about their configuration.
summary to bridge settings: 13 \% (15/119)
summary to progress: 86 \% (102/119)
summary to summary: 1 \% (2/119)

%how much time participants in aggregate spent in progress bar 
overall, participants spent 65\% of their time in the progress bar. 
e1 participants spent 28\% of their time in the progress bar. 
e2 participants spent 74\% of their time in the progress bar. 
e3 participants spent 63\% of their time in the progress bar. 
new participants spent 78\% of their time in the progress bar. 
old participants spent 57 \% of their time in the progress bar.

% how much time participants spent on average would be nice. (maybe I can do this later). 
%	i.e. the average participant in e1 spent x\% of their time in the progress bar.

% overall time spent configuring a proxy
overall, participants spent 18\% of their overall time configuring a proxy. 
e1 participants spent 16\% of their overall time configuring a proxy. 
e2 participants spent 10\% of their overall time configuring a proxy. 
e3 participants spent 21\% of their overall time configuring a proxy.  
new participants spent 7\% of their overall time configuring a proxy.  
old participants spent 25 \% of their overall time configuring a proxy.

% ``active'' time spent configuring a proxy
overall, participants spent 52\% of their active time configuring a proxy. 
e1 participants spent 22\% of their active time configuring a proxy. 
e2 participants spent 40\% of their active time configuring a proxy. 
e3 participants spent 57\% of their active time configuring a proxy.  
new participants spent 31\% of their active time configuring a proxy.  
old participants spent 58\% of their active time configuring a proxy.

> sum(proxy_edges$duration)/sum(active_edges$duration)*100
[1] 51.5947
> sum(proxy_edges[proxy_edges[,"env"]=="E1",]$duration)/sum(active_edges[active_edges[,"env"]=="E1",]$duration)*100
[1] 22.37932
> sum(proxy_edges[proxy_edges[,"env"]=="E2",]$duration)/sum(active_edges[active_edges[,"env"]=="E2",]$duration)*100
[1] 40.37673
> # e3 % on proxy screen ("active time")
> sum(proxy_edges[proxy_edges[,"env"]=="E3",]$duration)/sum(active_edges[active_edges[,"env"]=="E3",]$duration)*100
[1] 56.61874
> # new % on proxy screen ("active time")
> sum(proxy_edges[proxy_edges[,"version"]=="NEW",]$duration)/sum(active_edges[active_edges[,"version"]=="NEW",]$duration)*100
[1] 31.20091
> # old % on proxy screen ("active time")
> sum(proxy_edges[proxy_edges[,"version"]=="OLD",]$duration)/sum(active_edges[active_edges[,"version"]=="OLD",]$duration)*100
[1] 58.14161

% how much time participants spent on average during their ``active time'' would be nice (maybe I can do this later). 
% 	i.e. the average participant in new spent x\% of their active time configuring a proxy.

% looking at all factors' impact on success rate
A logistic regression model showing effects of censorship environment, interface version,
and recruitment pool on success finds that a difficult censorship environment is the most
significant factor in a participant failing. Xlab participants were more likely to succeed. 
Participants with the old version of the interface were more likely to fail.

@@

% looking at all factors' impact on time to completion
A linear regression model showing effects of censorship environment, interface version, 
and recruitment pool on success finds that a difficult censorship environment is the most
significant factor in taking a long time to complete the task. Participants with the old version
of the interface and participants recruited from Xlab were likely to take longer.
